quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-19 paper-quollr.Rmd
Updated trimesh figure configurations

```{r geom-outputs, fig.cap="The outputs of `geom_hexgrid` and `geom_trimesh` include: (a) a complete hexagonal grid, (b) a hexagonal grid that corresponds with the data, (c) a full grid based on centroid triangulation, and (d) a centroid triangulation grid that aligns with the data.", fig.align='center', fig.pos='H', eval=knitr::is_html_output()}

@@

```{r geom-outputs-pdf, fig.cap="The outputs of `geom\\_hexgrid` and `geom\\_trimesh` include: (a) a complete hexagonal grid, (b) a hexagonal grid that corresponds with the data, (c) a full grid based on centroid triangulation, and (d) a centroid triangulation grid that aligns with the data.", fig.align='center', fig.pos='H', eval=knitr::is_latex_output()}

@@

```{r limb-rmse, fig.cap="Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.", out.width="100%"}

>>>>

```{r geom-outputs, fig.cap="The outputs of `geom_hexgrid` and `geom_trimesh` include: (a) a complete hexagonal grid, (b) a hexagonal grid that corresponds with the data, (c) a full grid based on centroid triangulation, and (d) a centroid triangulation grid that aligns with the data.", fig.align='center', fig.pos='H', fig.height=5, fig.width=20, eval=knitr::is_html_output()}

@@

```{r geom-outputs-pdf, fig.cap="The outputs of `geom\\_hexgrid` and `geom\\_trimesh` include: (a) a complete hexagonal grid, (b) a hexagonal grid that corresponds with the data, (c) a full grid based on centroid triangulation, and (d) a centroid triangulation grid that aligns with the data.", fig.align='center', fig.pos='H', fig.height=5, fig.width=20, eval=knitr::is_latex_output()}

@@

```{r limb-rmse, fig.cap="Assessing which of the 6 NLDR layouts on the limb muscle data is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f). Layout d is perform well at large binwidth (where the binwidth is not enough to capture the data struture) and poorly as bin width decreases. Layout f is the best choice.", fig.pos='H', out.width="100%"}
